The Impact of Immutability on Class Size

### 2020-04-11 paper/article.tex
address off

% \documentclass[a4paper,UKenglish,cleveref, autoref]{lipics-v2019}
\documentclass[12pt]{article}
\title{The Impact of Immutability on Class Size}
\author{Yegor Bugayenko\\Huawei Technologies Co., Ltd.\\Russian Research Institute (RRI)\\\texttt{yegor.bugayenko@huawei.com}}{}{}
% \authorrunning{Yegor Bugayenko}
% \ccsdesc[100]{Software and its engineering~Object oriented languages}
% \keywords{Object-Oriented Programming, Immutability, NCSS}
\usepackage[utf8]{inputenc}
\usepackage[numbers]{natbib}
\bibliographystyle{plainnat}
\usepackage[inline]{enumitem}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{verbatimbox}
\usepackage{interval}
\usepackage{hyperref}
\usepackage{minted}
  \setminted{fontsize=\footnotesize}
  \setminted{breaklines}
  \usemintedstyle{bw}
\newcommand{\code}[1]{\texttt{#1}}
\newenvironment{nicetable}
  {\setlength{\parindent}{0em}\medskip\small}
  {\medskip}
\input{total}
\begin{document}
\raggedbottom
\maketitle

@@

Object immutability has been the subject of multiple researches since
the begining of object-oriented programming~\citep{hakonen1999,porat2000,lea2000}.
Even though, according to~\citet{potanin2013},
``the notion of immutability is not as straightforward as it might seem, and many
different definitions of immutability exist,'' most industry experts consider
immutability being a virtue of classes and objects in Java and other
object-oriented programming languages.

>>>>

% \documentclass[a4paper,UKenglish,cleveref, autoref]{lipics-v2019}
\documentclass[12pt]{article}
\title{The Impact of Immutability on Class Size}
\author{Yegor Bugayenko}{}{}
% \authorrunning{Yegor Bugayenko}
% \ccsdesc[100]{Software and its engineering~Object oriented languages}
% \keywords{Object-Oriented Programming, Immutability, NCSS}
\usepackage[utf8]{inputenc}
\usepackage[numbers]{natbib}
\bibliographystyle{plainnat}
\usepackage[inline]{enumitem}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{verbatimbox}
\usepackage{interval}
\usepackage{hyperref}
\usepackage{minted}
  \setminted{fontsize=\footnotesize}
  \setminted{breaklines}
  \usemintedstyle{bw}
\newcommand{\code}[1]{\texttt{#1}}
\newenvironment{nicetable}
  {\setlength{\parindent}{0em}\medskip\small}
  {\medskip}
\input{total}
\begin{document}
\raggedbottom
\maketitle

@@

Object immutability has been the subject of multiple researches since
the begining of object-oriented programming~\citep{hakonen1999,porat2000,lea2000,taivalsaari1993}.
Even though, according to~\citet{potanin2013},
``the notion of immutability is not as straightforward as it might seem, and many
different definitions of immutability exist,'' most industry experts consider
immutability being a virtue of classes and objects in Java and other
object-oriented programming languages.
